Figures and results for main manuscript

### 2021-01-04 analysis/reports/manuscript_main.Rmd
fig edits

  ggplot(example_fs3, aes(skew, ..ndensity..)) +
    geom_density() +
    geom_histogram(bins = 50) +
    theme_bw() +
    geom_vline(xintercept = c(example_fs3$skew_95[1], example_fs3$skew_min[1]), color = "red") +
    ggtitle("", subtitle = paste0("Breadth index (skewness): ", round((example_fs3$skew_95_ratio_1t[1]), 2))),

@@

  ggplot(example_fs2, aes(skew, ..ndensity..)) +
    geom_density() +
    geom_histogram(bins = 50) +
    theme_bw() +
    geom_vline(xintercept = c(example_fs2$skew_95[1], example_fs2$skew_min[1]), color = "red") +
    ggtitle("", subtitle =  paste0("Breadth index (skewness): ", round((example_fs2$skew_95_ratio_1t[1]), 2))),

  ggplot(example_fs, aes(rank, abund, group = sim, color = skew)) +
    geom_line(alpha = .1) +
    theme_bw() +
    scale_color_viridis_c(option = "plasma", end = .8) +
    ggtitle("Large community", subtitle = paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1]))) +
    theme(legend.position = "right"),

  ggplot(example_fs, aes(skew, ..ndensity..)) +
    geom_density() +
    geom_histogram(bins = 50) +
    theme_bw() +
    geom_vline(xintercept = c(example_fs$skew_95[1], example_fs$skew_min[1]), color = "red") +
    ggtitle("", subtitle =  paste0("Breadth index (skewness): ", round((example_fs$skew_95_ratio_1t[1]), 2)))

>>>>

  ggplot(example_fs3, aes(skew)) +
  #  geom_density() +
    geom_histogram(bins = 50) +
    theme_bw() +
    geom_vline(xintercept = c(example_fs3$skew_95[1], example_fs3$skew_min[1]), color = "red") +
    ggtitle("", subtitle = paste0("Breadth index (skewness): ", round((example_fs3$skew_95_ratio_1t[1]), 2))),

@@

  ggplot(example_fs2, aes(skew)) +
  #  geom_density() +
    geom_histogram(bins = 50) +
    theme_bw() +
    geom_vline(xintercept = c(example_fs2$skew_95[1], example_fs2$skew_min[1]), color = "red") +
    ggtitle("", subtitle =  paste0("Breadth index (skewness): ", round((example_fs2$skew_95_ratio_1t[1]), 2))),

  ggplot(example_fs, aes(rank, abund, group = sim, color = skew)) +
    geom_line(alpha = .1) +
    theme_bw() +
    scale_color_viridis_c(option = "plasma", end = .8) +
    ggtitle("Large community", subtitle = paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1]))) +
    theme(legend.position = "right") +
    ylim(0, 5000) +
    theme(axis.text.y = element_text(size = 6, angle = 60)),

  ggplot(example_fs, aes(skew)) +
   # geom_density() +
    geom_histogram(bins = 50) +
    theme_bw() +
    geom_vline(xintercept = c(example_fs$skew_95[1], example_fs$skew_min[1]), color = "red") +
    ggtitle("", subtitle =  paste0("Breadth index (skewness): ", round((example_fs$skew_95_ratio_1t[1]), 2)))
